\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}



\begin{document}

\begin{titlepage}

    \begin{center}
        
        {\LARGE
            Rip Off\\
            \vspace{0.5cm}
            \textbf{Efficient Estimation of Word Representations in
            Vector Space} (Original Word2Vec)
        }\\
        \vspace{1cm}
        \url{https://arxiv.org/pdf/1301.3781.pdf}
        
        \vfill
        
        {\large Md. Nafis Faiyaz}\\
        \today
        
    \end{center}
    
\end{titlepage}

\section{Authors, Year and Title}

\section{Are any of the authors familiar? Do I know their other works?}

\section{Key terms and concepts yet to learn}
    Huffman tree based hierarchical softmax, 
    Projection Layer,
    DistBlelief,
    Adagrad,
    New Log Linear Models,
    Equations for complexity in different architectures

\section{Previous research and ideas (Introduction)}

\section{Reasoing for performing this research (Introduction)}

\section{Objectives of the study}

\section{Equipment/software used (Methods)}

\section{Variables being measured in experimentation (Methods)}

\section{Statistical tests? Results of them (Methods/Results)}

\section{Main Findings (Results)}

\section{How do these results fit into context of other research and their 'field'? (Discussion)}

\section{Explanation of each figure and their significance}

\section{Reproducibile? Is source code available?}

\section{My thoughts on results. Do they seem valid?}

\end{document}