\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}

\begin{document}

\begin{titlepage}

    \begin{center}
        
        {\LARGE
            Summary\\
            \vspace{0.5cm}
            \textbf{A neural probabilistic language model} (Original Word2Vec)
        }\\
        \vspace{1cm}
        \url{https://arxiv.org/pdf/1301.3781.pdf}
        
        \vfill
        
        {\large Md. Nafis Faiyaz}\\
        \today
        
    \end{center}
    
\end{titlepage}

\section{Research Objectives}
    Introduce techniques to train high quality word vectors from a huge corpus with a low computational cost. They came up with continuous bag of words and skip-gram model.
    
\section{Dataset}
    Training: Google News corpus with 6B tokens. First evaluated models trained on subsets of the training data, with vocabulary restricted to the most frequent 30k words. 
    
    Testing: 8869 semantic and 10675 syntactic questions were created in two steps: ﬁrst, a list of similar word pairs was created manually. Then, a large list of questions is formed by connecting two word pairs. e.g. a list of 68 large American cities and the states they belong to, and formed about 2.5K questions by picking two word pairs at random. Multi-word entities (such as New York) are not present
    
\section{Methodology}
    Make a graph / pipeline (lucid chart)
    
\section{Experimental analysis}
    Setup and results
    
\section{Discussion}
    Contribution and future work    

\end{document}
